\LARGE \bf Stochastic Uncertainty Propagation in Power System Dynamics using Measure-valued Proximal Recursions

### 2021-06-27 Papers/Stochastic_Uncertainty_Propagation_TPS/JKO_Power_Systems_TPS.tex
updating Sec. V

\author{Abhishek~Halder,~\IEEEmembership{Member,~IEEE,} 
%\author{Abhishek~Halder,~\IEEEmembership{Member,~IEEE,}
Xinbo~Geng,~\IEEEmembership{Member,~IEEE,}
        Kenneth~F. Caluya,
        and~Pegah~Ojaghi% <-this % stops a space
\thanks{A. Halder and K.F. Caluya are with the Department of Applied Mathematics, University of California, Santa Cruz, CA 95064, USA, {\texttt{\{ahalder,kcaluya\}@ucsc.edu}}.}% <-this % stops a space
\thanks{X. Geng is with {\red{Edit next}} the Department of Applied Mathematics, University of California, Santa Cruz, CA 95064, USA, {\texttt{ahalder@ucsc.edu}}.} %
\thanks{P. Ojaghi is with the Department of Computer Science and Engineering, University of California, Santa Cruz, CA 95064, USA, {\texttt{pojaghi@ucsc.edu}}.}%
\thanks{This research was partially supported by the NSF award 1923278.}}% <-this % stops a space
%\thanks{Manuscript received April 19, 2005; revised August 26, 2015.}}
% The paper headers
%\markboth{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2015}%

@@

\begin{figure}[htpb]
\centering
\includegraphics[width=0.9\linewidth]{ProxSchmatic.pdf}
\caption{\small{A schematic of approximating the flow of the joint PDF trajectory $\rho(t,\bm{x})$ via the sequence $\{\varrho_{k}\}_{k\in\mathbb{N}}$ generated by a variational recursion over $\mathcal{P}_{2}\left(\mathbb{T}^{n}\times\mathbb{R}^{n}\right)$. The curve $\rho(t,\bm{x})$ solves a kinetic Fokker-Planck PDE initial value problem. While the joint PDFs are supported over the finite dimensional base manifold $\mathbb{T}^{n}\times\mathbb{R}^{n}$, the proximal updates $\{\varrho_{k}\}_{k\in\mathbb{N}}$ evolve over the infinite dimensional manifold $\mathcal{P}_{2}\left(\mathbb{T}^{n}\times\mathbb{R}^{n}\right)$.}}
\vspace*{-0.1in}
\label{fig:ProxSchematic}
\end{figure}

@@

\begin{figure}[htpb]
\centering
\includegraphics[width=0.95\linewidth]{ComputationalTimeSynthetic.png}
\caption{\small{The computational time for propagating the transient joint state PDFs over $\mathbb{T}^{20}\times\mathbb{R}^{20}$ for the simulation set up in Sec. \ref{subsec:NumSimSynthetic}.}}
\vspace*{-0.1in}
\label{fig:CompTimeSynthetic}
\end{figure}
\begin{figure}[htpb]
\centering
\includegraphics[width=0.95\linewidth]{RelativeErrorMeanMCVersusProxSynthetic.png}
\caption{\small{The relative error between the empirical mean (i.e., Monte Carlo estimate) $\bm{\mu}_{k}^{\text{MC}}\in\mathbb{T}^{20}\times\mathbb{R}^{20}$, and the mean $\bm{\mu}_{k}^{\text{Prox}}\in\mathbb{T}^{20}\times\mathbb{R}^{20}$ obtained using the proximal updates of the joint state PDFs, for the simulation set up in Sec. \ref{subsec:NumSimSynthetic}.}}
\vspace*{-0.1in}
\label{fig:RelErrSynthetic}
\end{figure}

@@

\begin{IEEEbiography}[{\includegraphics[height=1.25in]{Abhishek-Halder.jpg}}]{Abhishek
Halder}
(S'10-M'14) is an Assistant Professor in the Department of Applied Mathematics,
and is an affiliated faculty in the Department of Electrical and Computer Engineering at
University of California, Santa Cruz. Before that he held postdoctoral
positions in the Department of Mechanical and Aerospace Engineering at
University of California, Irvine, and in the Department of Electrical
and Computer Engineering at Texas A\&M University. He obtained his
Bachelors and Masters from Indian Institute of Technology Kharagpur in
2008, and Ph.D. from Texas A\&M University in 2014, all in Aerospace
Engineering. His research interests are in stochastic systems, control, learning and optimization with application focus on large scale cyber-physical
systems.
\end{IEEEbiography}

@@

\begin{IEEEbiography}{Xinbo Geng}
Biography text here.
\end{IEEEbiography}

>>>>

\author{Abhishek~Halder,~\IEEEmembership{Member,~IEEE,} 
%\author{Abhishek~Halder,~\IEEEmembership{Member,~IEEE,}
Xinbo~Geng,~\IEEEmembership{Member,~IEEE,}
        Kenneth~F. Caluya,
        and~Pegah~Ojaghi% <-this % stops a space
\thanks{A. Halder and K.F. Caluya are with the Department of Applied Mathematics, University of California, Santa Cruz, CA 95064, USA, {\texttt{\{ahalder,kcaluya\}@ucsc.edu}}.}% <-this % stops a space
\thanks{X. Geng is with the School of Electrical and Computer Engineering, Cornell University, Ithaca, NY 14850, USA, {\texttt{xg72@cornell.edu}}.} %
\thanks{P. Ojaghi is with the Department of Computer Science and Engineering, University of California, Santa Cruz, CA 95064, USA, {\texttt{pojaghi@ucsc.edu}}.}%
\thanks{This research was partially supported by the NSF award 1923278.}}% <-this % stops a space
%\thanks{Manuscript received April 19, 2005; revised August 26, 2015.}}
% The paper headers
%\markboth{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2015}%

@@

\begin{figure}[htpb]
\centering
\includegraphics[width=0.9\linewidth]{ProxSchmatic.pdf}
\caption{\small{A schematic of approximating the flow of the joint PDF trajectory $\rho(t,\bm{x})$ via the sequence $\{\varrho_{k}\}_{k\in\mathbb{N}}$ generated by a variational recursion over $\mathcal{P}_{2}\left(\mathbb{T}^{n}\times\mathbb{R}^{n}\right)$. The curve $\rho(t,\bm{x})$ solves a kinetic Fokker-Planck PDE initial value problem. While the joint PDFs are supported over the finite dimensional base manifold $\mathbb{T}^{n}\times\mathbb{R}^{n}$, the proximal updates $\{\varrho_{k}\}_{k\in\mathbb{N}}$ (shown as circled markers with no face-color) evolve over the infinite dimensional manifold $\mathcal{P}_{2}\left(\mathbb{T}^{n}\times\mathbb{R}^{n}\right)$.}}
\vspace*{-0.1in}
\label{fig:ProxSchematic}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.95\linewidth]{ComputationalTimeSynthetic.png}
\caption{\small{The computational time for propagating the transient joint state PDFs over $\mathbb{T}^{20}\times\mathbb{R}^{20}$ for the simulation set up in Sec. \ref{subsec:NumSimSynthetic}.}}
\vspace*{-0.1in}
\label{fig:CompTimeSynthetic}
\end{figure}
\begin{figure}[t]
\centering
\includegraphics[width=0.95\linewidth]{RelativeErrorMeanMCVersusProxSynthetic.png}
\caption{\small{The relative error between the empirical mean (i.e., Monte Carlo estimate) $\bm{\mu}_{k}^{\text{MC}}\in\mathbb{T}^{20}\times\mathbb{R}^{20}$, and the mean $\bm{\mu}_{k}^{\text{Prox}}\in\mathbb{T}^{20}\times\mathbb{R}^{20}$ obtained using the proximal updates of the joint state PDFs, for the simulation set up in Sec. \ref{subsec:NumSimSynthetic}.}}
\vspace*{-0.1in}
\label{fig:RelErrSynthetic}
\end{figure}

@@

\begin{IEEEbiography}[{\includegraphics[height=1.25in]{Abhishek-Halder.jpg}}]{Abhishek
Halder}
(S'10--M'14) is an Assistant Professor in the Department of Applied Mathematics,
and is an affiliated faculty in the Department of Electrical and Computer Engineering at
University of California, Santa Cruz. Before that he held postdoctoral
positions in the Department of Mechanical and Aerospace Engineering at
University of California, Irvine, and in the Department of Electrical
and Computer Engineering at Texas A\&M University. He obtained his
Bachelors and Masters from Indian Institute of Technology Kharagpur in
2008, and Ph.D. from Texas A\&M University in 2014, all in Aerospace
Engineering. His research interests are in stochastic systems, control, learning and optimization with application focus on large scale cyber-physical
systems.
\end{IEEEbiography}

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{XinboGeng.jpg}}]{Xinbo Geng} (S'13--M'20)
received his B.E. degree in Electrical Engineering from Tsinghua University, Beijing, China, in 2013. He received the M.S. and Ph.D. degrees from Department of Electrical and Computer Engineering, Texas A\&M University, College Station, TX, in 2015 and 2019, respectively.
He is a postdoctoral researcher jointly affiliated with Cornell University and Texas A\&M University since 2020.
He was a power system design and studies intern at National Renewable Energy Lab in 2016, a data analyst intern at ISO New England in 2017, a visiting student at UC Berkeley and MIT in 2018, and a visiting student at University of Wisconsin Madison in 2019.
His main research interest is decision making under uncertainties.
\end{IEEEbiography}
